Pillar 2 - Topic Modeling

### 2019-03-21 Pillar 2 - Topic Modeling.Rmd

```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA

@@

```{r function reorder_within & co., echo = FALSE}

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data, eval = TRUE}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

  data %>%
    count(
      `Course ID`,
      word
      ) %>%
    bind_tf_idf(
      term = word, 
      document = `Course ID`,
      n = n
      )

@@

##Ideal Number of Topics Package Test
To decide the number of topics to discover, we run three different tests.
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

}
```
We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
```{r description topics, cache = TRUE}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_description,
     file = "Output/LDA_ntopics.RDATA")

print(time.taken)
```

We run the test for overview, documeting its duration. 
```{r overview topics, cache = TRUE}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

print(time.taken)
```

We run the test for manuals, documenting its duration.
```{r manual topics, cache = TRUE}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_manual, result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

print(time.taken)
```

from 20, to 40, by 5 topics takes
22min for overview
11min for description
5.5hrs for manuals

We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}

load("Output/LDA_ntopics.RDATA")

result_description %>%
  FindTopicsNumber_plot

result_overview %>%
  FindTopicsNumber_plot

result_manual %>%
  FindTopicsNumber_plot

```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

@@

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
###Functions for models (get gamma, get beta, extract_dtm)
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

@@

The following functions allow us to inspect the distributions and get kw
```{r}
# FUNCTION
#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}

# get_top_match <- function(d_distribution){
#   print(!!sym(d_distribution))
# }

@@

```
###Training Models
```{r LDA fit, cache = TRUE, eval = TRUE}

test_topic_model <- tibble( #change to topic_model
  #repeat each topic number twice
  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5

  ) %>%
  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),
         DTM        = pmap(.l = list(Origin), .f = extract_dtm),

         #fit model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),

@@

         #selecting keywords
         kw = map(Beta, .f = get_kw)
         )

#View(test_topic_model)
test_topic_model
```
#DELETE LATERRRRRR- HELPER IMPORT
```{r}
load("Output/topic_model.RDATA")
```

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

@@

##Saving model_data:
For internal use:
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
```

#App
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

remove_words <- function(x){
  setdiff(x, not_include)
}

kw1 <- lapply(
  kw,
  remove_words
)

```
##Convenience vectors for APP
```{r for convenience}
# set seed
set.seed(1)

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

>>>>

#Setup
##Libraries
```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang) #quote
library(ldatuning) # ideal number of topics in LDA

@@

##Functions for internal faceting
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

##Loading data
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $overview, $description, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("output/data_pillar_2.RDATA")

# keep most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.

## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

  data %>%
    count(
      `Course ID`,
      word
      ) %>%
    bind_tf_idf(
      term = word, 
      document = `Course ID`,
      n = n
      )
}

@@

##Ideal Number of Topics Package Test
To decide the number of topics to discover, we run three different tests.
###Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

}
```
###Train
```{r package test on topics, cache = TRUE}
#Start timer
start.time <- Sys.time()

#
##apply my_FindTopicsNumber
result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))

#Stop timer
end.time <- Sys.time()
print(end.time - start.time)

#
##Save results
#save(result_topic_test,
#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
```
Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
* Overview:     22min 
* Description:  11min 
* Manuals:      5.5hrs

###Graph 
We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}
#load("Output/LDA_ntopics.RDATA")

result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

@@

###Functions for models (extract_dtm, get_distributions, perplexity)
The following functions are used as input in a map to compute and evaluate topic models. 
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

@@

The following functions allow us to inspect the results from our models(inspect distributions and get kw):
```{r}
 # get_top_match <- function(d_distribution){
 # 
 #  #save user input as string
 #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
 #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
 # 
 #  #Compute Case (Beta or Gamma, respectively)
 #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
 #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
 #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
 # 
 #  #
 #  ## DATA
 #  data.frame(d_distribution) %>%
 #    group_by(!!sym(grouping)) %>%
 #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
 #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
 #    group_by(!!sym(grouping)) %>%
 #    summarise(top = list(!!sym(objects_to_group)))
 # }

@@

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}

test_topic_model <- tibble( #CHANGE NAME TO: topic_model

  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5

  ) %>%
  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

         #Document Term Matrix
         DTM        = pmap(.l = list(Origin), .f = extract_dtm),

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),

@@

         #Select keywords
         kw = map(Beta, .f = get_kw)
         )

# Clean workspace

# rm(extract_dtm, get_distributions, my_perplexity,
#    get_top_terms_topic, get_top_topics_course, get_kw)

# test_topic_model
```

##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

@@

##Saving model_data:
We save our tibble with all the information.
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
```

#App
For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words}
clean_kw <- function(kw_list){

  #stopwords
  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")

  #remove stopwords
  kw <- setdiff(kw_list, kw_stopwords)
  #return
  return(kw[!is.na(kw)])

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App}
app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience}
# set seed
set.seed(1)

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort

```
## Saving files for APP
```{r app files}
# save(app_topic_model, course_all, course_following_semester,
#      file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){
